Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2024-06-17 lqg-strings.tex
Moved sections around to improve flow (DV+LdS)
Changed bimetric polyakov subsection title

\subsection{Modified Equations of Motion}\label{sec:modified-eom}

@@

\subsection{The Bimetric Polyakov Equations} \label{sec:bimetric-polyakov-eoms}

>>>>

\subsection{Worldsheet Kalb Ramond and Area Quantization} \label{sec:ws-kalb-ramond}

In the following we will

@@

\subsection{Modified Nambu Goto Equations of Motion}\label{sec:modified-eom}
